---
title: "google capstone 2"
author: "Amal"
date: "2024-04-02"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Install and load the tidyverse

```{r package}
options(repos = "https://cran.rstudio.com/")
 install.packages('tidyverse')
 library(tidyverse)
```
```{r Create data frame}
daily_activity <- read.csv("dailyActivity_merged.csv")
```

```{r next data frame}
sleep_day <- read.csv("sleepDay_merged.csv")
```

```{r take look the data }
head(daily_activity)
```
identify columns
```{r colnames}
colnames(daily_activity)
```


```{r}
head(sleep_day)
```

```{r}
colnames(sleep_day)
```

 How many unique participants are there in each dataframe? It looks like there may be more participants in the daily activity
dataset than the sleep dataset.
```{r}
n_distinct(daily_activity$Id)
n_distinct(sleep_day$Id)
```
 How many observations are there in each dataframe?
```{r}

nrow(daily_activity)
```
```{r}
nrow(sleep_day)
```
 What are some quick summary statistics we'd want to know about each data frame?
 For the daily activity dataframe:
```{r}

daily_activity %>%
select(TotalSteps,
TotalDistance,
SedentaryMinutes) %>%
summary()
```

# For the sleep dataframe:
```{r}
sleep_day %>%
select(TotalSleepRecords,
TotalMinutesAsleep,
TotalTimeInBed) %>%
summary()
```
 What's the relationship between steps taken in a day and sedentary minutes?
 How could this help inform the customer segments that we can market to?
 E.g. position this more as a way to get started in walking more?
Or to measure steps that you're already taking?
```{r}
ggplot(data=daily_activity, aes(x=TotalSteps, y=SedentaryMinutes)) + geom_point()
```
You might expect it to be almost completely linear - are there any unexpected trends?
```{r}
ggplot(data=sleep_day, aes(x=TotalMinutesAsleep, y=TotalTimeInBed)) + geom_point()
```

merging two dataset together
```{r}
combined_data <- merge(sleep_day, daily_activity, by="Id")
```

Take a look at how many participants are in this data set.
```{r}
n_distinct(combined_data$Id)
```

